Normalized expressions

### 2021-02-24 analysis/normalized.Rmd
Precise the preprocessing/postprocessing insertion of blocks

There are `r nb_call_sites` in the dataset.

@@

@@

>>>>

There are `r nb_call_sites` call sites in the dataset.

@@

```{r}
by_src_ref %>% datatable()
```

@@

# Complex blocks

`eval` can evaluate sometimes complex blocks.

```{r}
blocks <- E_cano %>% filter(has_block)

nb_blocks_call_sites <- blocks %>% pull(src_ref) %>% n_distinct()
```

There are `r nb_blocks_call_sites` such call sites.

`eval` is used to insert blocks of code inside the function, for instance as a preprocessing and postprocessing step. There are some examples in the VGAM package. In that case, `{` will be at the root of the AST.

```{r}
pre_post <- blocks %>% filter(topcall == "{")

nb_pre_post_call_sites <- pre_post %>% pull(src_ref) %>% n_distinct()
```

It happens in `r nb_pre_post_call_sites` call sites so most of the call sites with blocks.
